Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-07-20 ms.tex
a few corrections from BG and TH.

\author{Betsy Green?}
\affiliation{Steward Observatory, Tucson AZ 85721}

@@

We used the Python \texttt{photutils v0.3} \citep{bradley2016photutilsv0p3} package to centroid and extract fluxes of the \shStar\ and the reference stars.
We used a photometric aperture of 9 pixels (3.9") and a background annulus from 9 to 12 pixels (3.9" to 5.2") on all stars and nights.
12 stable reference stars with similar R band brightnesses were used to construct a reference time series to correct for variable telluric and instrument throughput.
The reference stars are identified Figure \ref{fig:refStars} across the 9.8\arcmin $\times$ 9.8 \arcmin\ Mont4K field of view.
These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \shStar.

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
\caption{Time series photometry for all stars and all nights nights.
The nights in July appear more strongly affected by cloud/and or seeing variations, whereas the two nights in June are stable to within a few percent.
All source radius, background start and background annulus end parameters were 9, 9 and 12 pixels respectively.}\label{fig:allNightallStar}
\end{centering}
\end{figure*}

>>>>

\author{Elizabeth Green}
\affiliation{Steward Observatory, Tucson AZ 85721}

@@

We used the Python \texttt{photutils v0.3} \citep{bradley2016photutilsv0p3} package to centroid and extract fluxes of the \shStar\ and the reference stars.
We used a photometric aperture of 9 pixels (3.9") and a background annulus from 9 to 12 pixels (3.9" to 5.2") on all stars and nights.
12 stable reference stars with similar R band brightnesses were used to construct a reference time series to correct for variable telluric and instrument throughput.
The reference stars are identified Figure \ref{fig:refStars} across the 9.7\arcmin $\times$ 9.7 \arcmin\ Mont4K field of view.
These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \shStar.

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
\caption{Time series photometry for all stars and all nights.
The nights in July appear more strongly affected by cloud/and or seeing variations, whereas the two nights in June are stable to within a few percent.
All source radius, background start and background annulus end parameters were 9, 9 and 12 pixels respectively.}\label{fig:allNightallStar}
\end{centering}
\end{figure*}
